### 2018-06-22 Stickleback_Paper.tex
latest =
added matplotlib plots

\subsubsection{Migration is Mixing}

@@

\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=01.0\linewidth]{PhenotypeDist}
  		\caption{A boat.}
  		\label{fig:boat1}
	\end{center}
\end{figure}

Across increasing parameters of migration, we observed more gene flow across the populations. 
As can be seen in Figure (neutral fst figure)
$F_{st}$ values for neutral Alleles steadily decline between all sets of populations as 
migration increases, this illustrates less difference between sections of the genome which are not acted up 
upon by selection, in all populations.
Additionally, Standing Genetic Variance \todo{computed as?}
(Seen in SGV Figure)
values in the marine population steady increased with migration which suggests that more alleles from the 
lakes surrounding were exporting alleles into the marine individuals.
\todo{Something about SGV rates for the the other population}

@@

\subsubsection{migration affects the speed of adaptation}

%FIGURES THAT SHOW THIS:
%-Time to adaptation

@@

\subsubsection{sharing of freshwater adapted alleles}

%FIGURES THAT SHOW THIS:
%-MPAA / IND
%-Total/Avg shared

@@

\subsubsection{We see Migration Load after a certain threshold of migration}

@@

\subsubsection {There is a Qualitative Threshold of migration rates}

@@

\subsubsection {Low Recombination Causes Clustering}

\begin{comment}
%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
Across migration rates we observe a large difference in:
gene flow, 
$F_{st}$ values,
amount of time until adaptation,
sharing of solutions (haplotytes?),
$SGV$,
and, migration load. 
we run multiple simulations across a range of migration rates starting at $5e-5$ and increasing by
one order of magnitude up to $.05$. 
With the marine and freshwater both at a population size 2000,
this represents exactly $1/10_{th}$, $1$, $10$, and $100$ migrants per generation, respectively.

>>>>

\subsubsection*{Migration is Mixing}

@@

\begin{figure}[htb]
	\begin{center}
  		\includegraphics[width=01.0\linewidth]{matplotlib/Fst.png}
  		\caption{A boat.}
  		\label{fig:boat1}
	\end{center}
\end{figure}

Across increasing parameters of migration, we observed more gene flow across the populations. 
As can be seen in Figure (neutral fst figure)
$F_{st}$ values for neutral alleles steadily decline between all sets of populations as 
migration increases, this illustrates less difference between sections of the genome which are not acted up 
upon by selection, in all populations.
Additionally, Standing Genetic Variance \todo{computed as?}
(Seen in SGV Figure)
values in the marine population steady increased with migration which suggests that more alleles from the 
lakes surrounding were exporting alleles into the marine individuals.
\todo{Something about SGV rates for the the other population}

@@

\subsubsection*{migration affects the speed of adaptation}

%FIGURES THAT SHOW THIS:
%-Time to adaptation
%\begin{figure}[h!tb]
%	\begin{center}
%  		\includegraphics[width=01.0\linewidth]{???}
%  		\caption{A boat.}
%  		\label{fig:boat1}
%	\end{center}
%\end{figure}

@@

\subsubsection*{sharing of freshwater adapted alleles}

%FIGURES THAT SHOW THIS:
%-MPAA / IND
%-Total/Avg shared
\begin{figure}[h!tb]
	\begin{center}
  		\includegraphics[width=0.8\linewidth]{matplotlib/MPFAI.png}
  		\caption{A boat.}
  		\label{fig:boat2}
	\end{center}
\end{figure}

@@

\subsubsection*{We see Migration Load after a certain threshold of migration}

@@

\subsubsection*{There is a Qualitative Threshold of migration rates}

@@

\subsubsection*{Low Recombination Causes Clustering}

\begin{comment}
%--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------
%SHOULD PROBABLY JUST DELETE ALL THIS. V UNORGANIZED.
Across migration rates we observe a large difference in:
gene flow, 
$F_{st}$ values,
amount of time until adaptation,
sharing of solutions (haplotytes?),
$SGV$,
and, migration load. 
we run multiple simulations across a range of migration rates starting at $5e-5$ and increasing by
one order of magnitude up to $.05$. 
With the marine and freshwater both at a population size 2000,
this represents exactly $1/10_{th}$, $1$, $10$, and $100$ migrants per generation, respectively.
